---
title: "ANA-515 Assignment 2"
author: "Shahnawaz Shaik"
date: '2022-06-20'
output: html_document
---

```{r get-data, include = FALSE}
library(readxl)
EVDatabase <- read_excel("C:\\mydata\\Cheapestelectriccars-EVDatabase.xls")

newdata <- EVDatabase
```

```{r}
library(dplyr)
```

#this next line is creating a subset called 'SUV' of the gun_data dataset where the age is equal or greater to 65
```{r}
SUV <- newdata %>% 
  filter(NumberofSeats >= 5)
summary(SUV)

AllWheel<-filter(newdata, Drive=="All Wheel Drive")
```

#Let's just see the Name and Acceleration columns
```{r}
select(newdata, Name, Acceleration)
#Let's arrange our data, Names of the cars by Range
arrange(newdata, Name, Range)
```

#This next chunk is inline code. Inline code puts the text with the output of the function in the document.


```{r}
#this makes a new data.frame called text_tbl with two columns, Names and Description
text_tblnew <- data.frame( 
Names = c("Name", "Subtitle", "Acceleration","TopSpeed","Efficiency","FastChargeSpeed","Drive","NumberofSeats","PriceinGermanyx","PriceinUK"), 
          Description = c("Name of the car","Subtitle","Acceleration of the car","TopSpeed of the car","Efficiency of the car","FastChargeSpeed of the car","Drive of the car","NumberofSeats of the car","PriceinGermanyx of the car","PriceinUK of the car")
) 

#prints the table
text_tblnew 

#kable will make the table look better
knitr::kable(text_tblnew, "pipe")
```

# picking three columns to use summary function:
```{r}
data_pick3 <- select(newdata, "Acceleration","TopSpeed","Efficiency")
```

Produce a summary of the subset:
```{r, include = TRUE}
Summarytable<-summary(data_pick3) #creates the summary
print(Summarytable)
```


# Enhanced Histogram of cars vs seats
# by Number of Car Cylinders
```{r, include = TRUE}
x <- newdata$Name
y <- newdata$NumberofSeats

hist(y,
     main="Distribution of EV Cars by number of seats",
     xlab="Number of Seats in a car",
     col="blue")

# Plot with main and axis titles
# Change point shape (pch = 19) and remove frame.
# Drawing 
# Gun deaths by age 

library(ggplot2)
SUV %>% 
ggplot(aes(NumberofSeats)) + 
geom_freqpoly(binwidth = 1)
```
